To Do List

### 2019-08-01 Papers.Rmd
Add LSTM TAD prediction paper

>>>>

- Rozenwald, Michal, Ekaterina Khrameeva, Grigory Sapunov, and Mikhail Gelfand. “Prediction of 3D Chromatin Structure Using Recurrent Neural Networks.” In 2018 IEEE International Conference on Bioinformatics and Biomedicine (BIBM), 2488–2488. IEEE, 2018. - Prediction of TAD boundaries using penalized regressions and RNNs. RNN with LSTM units captures the sequential ordering of the genome, distance. Drosophila data, Armatus for TAD calling. PyTorch and Keras implementation.
